Two-Dimensional Vesicle Hydrodynamics from Hydrophobic Attraction Potential

### 2021-09-21 doc/main_jfm.tex
edits up to 4.2.2

\hypersetup{
    colorlinks = true,
    urlcolor   = blue,
    citecolor  = black,
}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newcommand{\RomanNumeralCaps}[1]
\linenumbers

@@

%\title{Two-Dimensional Vesicles Under External Flow via Integral Equation Method}
\title{Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations}
%\author{Alan N. Jones\aff{1}
%  \corresp{\email{JFMEditorial@cambridge.org}},
%  H.-C. Smith\aff{1}
% \and J.Q. Long\aff{2}}
%
%\affiliation{\aff{1}STM Journals, Cambridge University Press, The Printing House, Shaftesbury Road, Cambridge CB2 8BS, UK
%\aff{2}DAMTP, Centre for Mathematical Sciences, Wilberforce Road, Cambridge CB3 0WA, UK}

@@

\begin{abstract}
  In this work, we study the dynamics of many-body systems immersed in a
  viscous fluid with a specified interparticle force. In particular, we
  apply a hydrophobic attraction potential (HAP) using a Janus type
  granular system to model lipid bilayer membranes. Coupling with an
  efficient integral equation method for rigid bodies in Stokes flow and
  a previous developed HAP solver, the deformations of a two-dimensional
  vesicle such as tank-treading motion and membrane ruptures can be
  observed under different values of the shear rate. Moreover, an
  efficient integral equation method is adopted for solving the screened
  Laplace equation and the mobility problem where it can accurately
  calculate hydrophobic and hydrodynamic interactions between near
  touched boundaries.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{Figure0_Wrapper.pdf}
\end{center}
\caption{Panel (a) illustrates the domain and boundary conditions for the mobility problem. 
The color map in panels (b) - (e) is the solution $u$ of \eqref{eq:SL}. Red indicates a high degree of hydrophobicity ($u = 1$) 
while blue indicates no hydrophobicity ($u = 0$).
Particles self-assemble into vesicle bilayers (panel (b)) and eventually  
arrange along inner and outer leaflets (panel (c)). The curve $C_M$ is the midplane curve which has 
length $L$ and surrounds a region of area $A$.  Initially stretched vesicles relax to equilibrium 
with fluid flow across the bilayer. The study considers a single vesicle in background flows such as shear flow (panel (d))
and hydrodynamic vesicle-vesicle interactions (panel (e)).}
\label{fig:figure0}
\end{figure}

\section{Governing Equations\label{sec:governing_eqs}}
\subsection{\label{mobility}Mobility Problem}
We consider an $N_b$-many body collection of Janus particles suspended
in a two-dimensional unbounded domain $\Omega$. The boundary of each
particle is denoted by $\Gamma_i$ so that $\bd \Omega = \Gamma_1 \cup
\Gamma_2 \cup \cdots \cup \Gamma_{N_b}$. Assuming the inertial terms are negligible, the
governing equations are
\begin{alignat}{3}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
    && \xx \in \Omega, \\
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
\end{alignat}
%
where $\uu$ is the velocity, $\mu$ is the constant viscosity, $p$ is the
pressure, and $\uu_\infty$ is the background flow. Since each particle
$\Gamma_i$ with center $\aa_i$ is a rigid body, its velocity satisfies 
\begin{align}
  \vv(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad 
    \xx \in \Gamma_i,
\end{align}
where $\vv_i$ is its translational velocity and $\omega_i$ is its
angular velocity. Here, $\langle x, y \rangle^{\perp} = \langle -y, x
\rangle$. Therefore, the no-slip boundary condition on each particle is
\begin{align}
  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad
    \xx \in \Gamma_i.
\end{align}
To determine the translational and angular velocities of each particle,
we define imposed forces $\FF_i$ and torques $T_i$ acting on each
particle. Since the small particles are intertialess, force balance
gives 
\begin{alignat}{2}
  \label{eq:force}
  \FF_i &+ \int_{\Gamma_i} \ssigma \cdot \nnu_i \, \dif s = \mathbf{0},
  && i=1,\ldots,N_b,\\
  \label{eq:torque}
  T_i &+ \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
    (\ssigma \cdot \nnu_i) \, \dif s = 0, \qquad && i=1,\ldots,N_b,
\end{alignat}
where $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
\right)$ is the hydrodynamic stress tensor (pressure tensor) and
$\nnu_i$ is the particle outward normal. The process of finding the
translational and angular velocities given the forces and torques is
referred to as the mobility problem.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Imposed Forces}
The imposed forces and torques contain two parts. The first part comes
from the hydrophobic attraction potential (HAP). This potential was
introduced in~\cite{Fu20} and models hydrophobic attraction by solving
the screened Laplace equation boundary value problem
\begin{alignat}{2}
  \label{eq:SL}
-\rho^2 \Delta u + u &=0,            && \xx \in \Omega,\\
\label{eq:SLbc}
u(\xx) &= f_i(\xx),\qquad  && \xx \in \Gamma_i,\; i=1,\ldots,N_b \\
\label{eq:SLff}
u &\to 0,                          &&|\xx| \to \infty,
\end{alignat}
where $0 \leq f_i \leq 1$ is a material label with $f_i = 0$,
respectively $1$, representing hydrophilic, respectively hydrophobic,
portions of the surface. We assume that the $f_i$ and $\Gamma_i$ are
smooth. The parameter $\rho$ is the decay length of attraction. The
forces and torques for this attraction are 
\begin{align}
  \label{eq:hydrophobicAttraction}
  \FF_i^{\text{hydro}} = \int_{\Gamma_i} {\bf T}\cdot \nnu_i \, \dif s, 
    \quad 
  T_i^{\text{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot ({\bf T} \cdot \nnu_i) \dif s,
\end{align}
where
\begin{align}
  \label{eq:stress}
\mathbf{T}
= \gamma\rho^{-1}u^2 \mathbf{I} + 2\rho\gamma \left(\tfrac{1}{2}|\nabla
  u|^2 \mathbf{I} - \nabla u  \nabla u^T\right)
\end{align}
is the hydrophobic stress tensor. The parameter $\gamma$ is
the interfacial
tension. The forces $\FF_i^{\text{hydro}}$ and torques
$T_i^{\text{hydro}}$ are responsible for forming particle aggregates
that partially sequester the hydrophobic portions of the particle
surface.

The second part of the imposed forces and torques comes from repulsion
between proximal particles. Given a pair particles indexed with $i$ and
$j$, we find the two points $\tilde{\xx}_i \in \Gamma_i$ and
$\tilde{\xx}_j \in \Gamma_j$ that are closest to one another. We then
define the repulsion force and torque
\begin{align}
  \label{eq:REPULforce}
  \FF_i^{\text{repul}} &= \sum_{j \neq i} 
    \frac{\tilde{\xx}_i - \tilde{\xx}_j}
    {|\tilde{\xx}_i - \tilde{\xx}_j|} 
    P'(|\tilde{\xx}_i - \tilde{\xx}_j|), \\
  \label{eq:REPULtorque}
  T_i^{\text{repul}} &= \sum_{j \neq i} 
    (\tilde{\xx}_i - \aa_i)^{\perp} \cdot 
    \frac{\tilde{\xx}_i - \tilde{\xx}_j}
    {|\tilde{\xx}_i - \tilde{\xx}_j|} 
    P'(|\tilde{\xx}_i - \tilde{\xx}_j|).
\end{align}
The repulsion profile $P(r)$ is zero for distances $r$ larger than a
repulsion length scale $\rho_0$. As such,~\eqref{eq:REPULforce}
and~\eqref{eq:REPULtorque} ignore particles $\Gamma_j$ outside a
tubular neighborhood of $\Gamma_i$. For $0 \leq r < \rho_0,$ we use
$P(r) = M(1 - \sin(r/\rho_0))$ where $M$ is sufficiently large to
prevent particle collisions. Then, the total imposed force and torque
are
\begin{align}
  \FF_i = \FF_i^{\text{hydro}} + \FF_i^{\text{repul}},\quad
  T_i = T_i^{\text{hydro}} + T_i^{\text{repul}}, \qquad
  i=1,\ldots,N_b.
\end{align}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Time Marching}
By solving the mobility problem, we obtain translational and angular
velocities of the $N_b$-body system. A second-order Adams-Bashforth
scheme updates the particle positions and orientations. By including the
repulsion force~\eqref{eq:REPULforce} and
torque~\eqref{eq:REPULtorque}, particle collisions are avoided even
when using a relatively large time step.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{HAP Boundary Integral Equation}
Similar to our previous work (\cite{Fu20}), we represent the HAP as a
double-layer potential
\begin{align}
  \label{eq:HAP_DLP}
  u(\xx) = \frac{1}{2\pi} \int_{\bd\Omega} \pderiv{}{\nnu_\yy}
    K_0 \left(\frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) \, \dif s_\yy,
    \quad \xx \in \Omega,
\end{align}
where $K_0$ is the zeroth-order modified Bessel function of the first
kind and the integral is taken in the sense of principle value whenever $\xx \in \partial \Omega$. 
By requiring that the density function $\sigma$ satisfies the
second-kind integral equation
\begin{equation}
\label{eq:screenedSKIE}
  f(\xx) = \frac{1}{2}\sigma(\xx) + 
    \frac{1}{2\pi}\int_{\bd\Omega} \pderiv{}{\nnu_\yy}
    K_0 \left(\frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) \, \dif s_\yy,
    \quad \xx \in \bd\Omega,
\end{equation}
the HAP double-layer potential~\eqref{eq:HAP_DLP} satisfies the screened
Laplace equation~\eqref{eq:SL}--\eqref{eq:SLff}. After
discretizing~\eqref{eq:screenedSKIE}, the result is a $NN_b \times NN_b$
linear system that is solved with block-diagonal preconditioned GMRES.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Mobility Problem Boundary Integral Equation}
Following previous work of~\cite{Lukas19}, we use the velocity
representation of~\cite{pow-mir1987}. In particular, we write the
velocity as the sum of a double-layer potential and $N_b$ Stokeslets and
Rotlets
\begin{align}
  \label{eq:velocity}
  \uu(\xx) = \uu_\infty(\xx) + \DD[\eeta](\xx) + 
    \sum_{i=1}^{N_b} \left(\SS(\xx,\aa_i) \FF_i + 
    \RR(\xx,\aa_i) T_i\right), \quad \xx \in \Omega.
\end{align}
The double-layer potential is
\begin{align}
  \DD[\eeta](\xx) = \frac{1}{\pi} \int_{\bd\Omega} 
    \frac{\rr \cdot \nnu}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
    \eeta(\yy) \, \dif s_\yy,
\end{align}
where $\rr = \xx - \yy$ and $\rho = |\rr|$. The Stokeslet and Rotlet
centered at $\aa_i$ are
\begin{align}
  \SS(\xx,\aa_i)\FF_i &= \frac{1}{4\pi} \left(-\log \rho + 
    \frac{\rr \otimes \rr}{\rho^2}\right) \FF_i, \\
  \RR(\xx,\aa_i)T_i &= \frac{1}{4\pi} \frac{\rr^\perp}{\rho^2} T_i,
\end{align}
respectively, where $\rr = \xx - \aa_i$ and $\rho = |\rr|$. The
Stokeslet is torque-free and has force $\FF_i$ while the Rotlet is
force-free and has torque $T_i$. Therefore, the
velocity~\eqref{eq:velocity} satisfies the total force~\eqref{eq:force}
and torque~\eqref{eq:torque} conditions if the double-layer potential
$\DD[\eeta]$ is force- and torque-free.  Matching the limit
of~\eqref{eq:velocity} with the rigid body motion, and imposing that
$\DD[\eeta]$ is force- and torque-free, the density function $\eeta$,
translational velocity $\vv_i$, and angular velocity $\omega_i$ satisfy
\begin{alignat}{3}
  \nonumber
  \vv_i + \omega_i (\xx - \aa_i)^\perp &= \uu_\infty(\xx)
    -\frac{1}{2} \eeta(\xx) + \DD[\eeta](\xx) \\
  \label{eq:SKIE}
    + \sum_{j=1}^{N_b} &
    \left(\SS(\xx,\aa_j) \FF_j + \RR(\xx,\aa_j) T_j\right),
    \quad &&\xx \in \Gamma_i,\: i=1,\ldots,N_b, \\
  \label{eq:mobility1}
  \int_{\bd\Gamma_i} \eeta \cdot \nnu_i \, \dif s &= {\bf 0}, 
  &&i = 1,\ldots,N_b, \\
  \label{eq:mobility2}
  \int_{\bd\Gamma_i} \eeta\times(\xx-\aa_i)^\perp \cdot \nnu_i \, \dif s &= 0,
  &&i = 1,\ldots,N_b.
\end{alignat}

After discretizing and applying appropriate quadrature rules, the result
is a $(2NN_b + 3N_b) \times (2NN_b + 3N_b)$ linear system that we solve
with block-diagonal preconditioned GMRES. We note that other BIE
formulations of the mobility problem use single-layer potentials
(\cite{cor-gre-rac-vee2017, rac-gre2016}) or a combination of single-
and double-layer potentials (\cite{cor-vee2018}).

We validated our solver for \eqref{eq:SKIE}-\eqref{eq:mobility2} using a
single elliptical particle suspended in a background shear flow (see
\S~\ref{sec:ves_in_shear}). Hydrophobic attraction and repulsion are
zero for a single particle. The angle of the ellipse's major axis coming
from the integral equation method was in complete agreement with the
theoretical, Jeffrey orbit time-course (\cite{jef1922}).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Calculating the Hydrophobic Force}
\label{subsec:calculating_force}
Once \eqref{eq:screenedSKIE} has been solved for $\sigma$, we need to
evaluate the integrals~\eqref{eq:hydrophobicAttraction} which are the
HAP forces and torques. These integrals involve the
stress~\eqref{eq:stress} which contains a singular integral for the
gradient of the double-layer potential. To avoid singular integrals, we
first define
\begin{align}
  \label{eq:uidef}
  v_i(\xx) = u(\xx) - u_i(\xx),
\end{align}
where
\begin{align}
  u_i(\xx) &= \frac{1}{2\pi} \int_{\Gamma_i} \pderiv{}{\nnu_\yy}
    K_0 \left(\frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) \, \dif s_\yy,
    \quad \xx \in \mathbb{R}^2.
\end{align}
That is, $v_i(\xx)$ is the double-layer potential~\eqref{eq:HAP_DLP}
with $\Gamma_i$ excluded from $\bd\Omega$. Having defined $v_i$, we can
show that
\begin{align}
  \label{eq:recipforcetorque}
  \FF_i^{\text{hydro}} = \int_{\Gamma_i} \JJ_i \,\dif s,\quad
  T_i^{\text{hydro}}    = \int_{\Gamma_i} 
    (\xx - \aa_i)^{\perp} \cdot \JJ_i  \,\dif s,
\end{align}
where
\begin{align}
  \label{eq:jumpstress1}
  \JJ_{i} = 2\gamma\rho^{-1} \sigma v_i \nnu + 
    2\gamma\rho \frac{d\sigma}{ds} \frac{dv_i}{ds} \nnu -
    2\gamma\rho \frac{d\sigma}{ds} \frac{dv_i}{d\nnu} \ttau.
\end{align}
Here, $\ttau$ and $\frac{d}{ds}$ are the unit tangent and arc length
derivative for $\Gamma_i$, respectively, and $\nnu$ is the unit normal.
The advantage in using~\eqref{eq:recipforcetorque} over
using~\eqref{eq:hydrophobicAttraction} is that the components $\sigma$,
$v_i$, $\frac{d\sigma}{ds}$, and $\frac{dv_i}{ds}$ of $\JJ_i$ are smooth
functions, whereas the components of \eqref{eq:stress} are singular
integrals.

@@

\subsection{Self-Assembly and Relaxation}

>>>>

\hypersetup{
    colorlinks = true,
    urlcolor   = blue,
    citecolor  = black,
}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\newcommand{\RomanNumeralCaps}[1]
\linenumbers

@@

%\title{Two-Dimensional Vesicles Under External Flow via Integral Equation Method}
\title{Two-Dimensional Vesicle Hydrodynamics from Hydrophobic Attraction Potential}
%\title{Hydrodynamics of Amphiphilic Particles in Background Flows}
%\author{Alan N. Jones\aff{1}
%  \corresp{\email{JFMEditorial@cambridge.org}},
%  H.-C. Smith\aff{1}
% \and J.Q. Long\aff{2}}
%
%\affiliation{\aff{1}STM Journals, Cambridge University Press, The Printing House, Shaftesbury Road, Cambridge CB2 8BS, UK
%\aff{2}DAMTP, Centre for Mathematical Sciences, Wilberforce Road, Cambridge CB3 0WA, UK}

@@

\begin{abstract}
  We develop a new model, to our knowledge,  for the hydrodynamics of amphiphilic particles in background flows. 
  In this work, we study the dynamics of many-body systems immersed in a
  viscous fluid with a specified interparticle force. In particular, we
  apply a hydrophobic attraction potential (HAP) using a Janus type
  granular system to model lipid bilayer membranes. Coupling with an
  efficient integral equation method for rigid bodies in Stokes flow and
  a previous developed HAP solver, the deformations of a two-dimensional
  vesicle such as tank-treading motion and membrane ruptures can be
  observed under different values of the shear rate. Moreover, an
  efficient integral equation method is adopted for solving the screened
  Laplace equation and the mobility problem where it can accurately
  calculate hydrophobic and hydrodynamic interactions between near
  touched boundaries.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{Figure0_Wrapper.pdf}
\end{center}
\caption{Panel (a) illustrates the domain and boundary conditions for the mobility problem. 
The color map in panels (b) - (e) is the solution $u$ of \eqref{eq:SL}. Red is for $u = 1$
and blue is for $u = 0$.
Particles self-assemble into vesicle bilayers (panel (b)) and eventually  
arrange along inner and outer leaflets. In panel (c), $C_M$ is the midplane curve,
$A$ is the enclosed area, and $L$ is the arc length.  Initially stretched vesicles relax to equilibrium 
with fluid flow across the bilayer. The study considers a single vesicle in background flows such as shear flow (panel (d))
and hydrodynamic vesicle-vesicle interactions (panel (e)).}
\label{fig:figure0}
\end{figure}

\section{Governing Equations\label{sec:governing_eqs}}
\subsection{\label{mobility}Mobility Problem}
The objective is to study the hydrodynamics of JP vesicles in background flows. 
We consider an $N_b$-many body collection of JP suspended
in a two-dimensional unbounded domain $\Omega$. 
The boundary of each particle is denoted by $\Gamma_i$ so that $\bd \Omega = \Gamma_1 \cup
\Gamma_2 \cup \cdots \cup \Gamma_{N_b}$ (Figure \ref{fig:figure0}a). 
Assuming the inertial terms are negligible, the governing equations are
\begin{alignat}{3}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
    && \xx \in \Omega, \\
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
\end{alignat}
%
where $\uu$ is the velocity, $p$ is the
pressure, $\uu_\infty$ is the background flow, and $\mu$ is the constant viscosity. 
Since each particle $\Gamma_i$ with center $\aa_i$ is a rigid body, its velocity satisfies 
\begin{align}
  \vv(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad 
    \xx \in \Gamma_i,
\end{align}
where $\vv_i$ is its translational velocity and $\omega_i$ is its
angular velocity. Here, $\langle x, y \rangle^{\perp} = \langle -y, x
\rangle$. Therefore, the no-slip boundary condition on each particle is
\begin{align}
\label{eq:rigid_bc}
  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad
    \xx \in \Gamma_i.
\end{align}
To determine the translational and angular velocities of each particle,
we define imposed forces $\FF_i$ and torques $T_i$ acting on each
particle. Since the small particles are inertialess, force balance
gives 
\begin{alignat}{2}
  \label{eq:force}
  \FF_i &- \int_{\Gamma_i} \ssigma \cdot \nnu \, \dif s = \mathbf{0},
  && i=1,\ldots,N_b,\\
  \label{eq:torque}
  T_i &- \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
    (\ssigma \cdot \nnu) \, \dif s = 0, \qquad && i=1,\ldots,N_b,
\end{alignat}
where $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
\right)$ is the hydrodynamic stress tensor (pressure tensor) and
$\nnu_i$ is the particle outward normal. The process of finding the
translational and angular velocities given the forces and torques is
referred to as the mobility problem.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Imposed Forces}
The imposed forces and torques contain two parts: hydrophobic attraction and repulsion. 
The hydrophobic attraction potential was introduced by ~\cite{Fu20} and is responsible for forming particle aggregates
that sequester their hydrophobic surface regions (Figure \ref{fig:figure0}b).
We model hydrophobic attraction by solving
the screened Laplace equation boundary value problem
\begin{alignat}{2}
  \label{eq:SL}
-\rho^2 \Delta u + u &=0,            && \xx \in \Omega,\\
\label{eq:SLbc}
u(\xx) &= f_i(\xx),\qquad  && \xx \in \Gamma_i,\; i=1,\ldots,N_b \\
\label{eq:SLff}
u &\to 0,                          &&|\xx| \to \infty,
\end{alignat}
where $0 \leq f_i \leq 1$ is a material label with $f_i = 0$,
respectively $1$, representing hydrophilic, respectively hydrophobic,
portions of the surface. We assume that the $f_i$ and $\Gamma_i$ are
smooth. The parameter $\rho > 0$ is the decay length of attraction. The
forces and torques of attraction are 
\begin{align}
  \label{eq:hydrophobicAttraction}
  \FF_i^{\text{hydro}} = \int_{\Gamma_i} {\bf T}\cdot \nnu \, \dif s, 
    \quad 
  T_i^{\text{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot ({\bf T} \cdot \nnu) \dif s,
\end{align}
where
\begin{align}
  \label{eq:stress}
\mathbf{T}
= \gamma\rho^{-1}u^2 \mathbf{I} + 2\rho\gamma \left(\tfrac{1}{2}|\nabla
  u|^2 \mathbf{I} - \nabla u  \nabla u^T\right)
\end{align}
is the hydrophobic stress tensor and $\gamma > 0$ is
the interfacial
tension.

The second part of the imposed forces and torques comes from repulsion
between proximal particles. Given a pair particles indexed with $i$ and
$j$, we find the two points $\tilde{\xx}_i \in \Gamma_i$ and
$\tilde{\xx}_j \in \Gamma_j$ that are closest to one another (Figure \ref{fig:figure0}a). We then
define the repulsion force and torque
\begin{align}
  \label{eq:REPULforce}
  \FF_i^{\text{repul}} &= \sum_{j \neq i} 
    \frac{\tilde{\xx}_i - \tilde{\xx}_j}
    {|\tilde{\xx}_i - \tilde{\xx}_j|} 
    P'(|\tilde{\xx}_i - \tilde{\xx}_j|), \\
  \label{eq:REPULtorque}
  T_i^{\text{repul}} &= \sum_{j \neq i} 
    (\tilde{\xx}_i - \aa_i)^{\perp} \cdot 
    \frac{\tilde{\xx}_i - \tilde{\xx}_j}
    {|\tilde{\xx}_i - \tilde{\xx}_j|} 
    P'(|\tilde{\xx}_i - \tilde{\xx}_j|).
\end{align}
The repulsion profile $P(r)$ is set to zero for distances $r$ larger than a
repulsion length scale $\rho_0$. As such,~\eqref{eq:REPULforce}
and~\eqref{eq:REPULtorque} ignore particles outside a
$\rho_0$-tubular neighborhood of $\Gamma_i$. For $0 \leq r < \rho_0,$ we use
$P(r) = M(1 - \sin(r/\rho_0))$ where $M$ is sufficiently large to
prevent particle collisions. Then, the total imposed force and torque
are
\begin{align}
  \FF_i = \FF_i^{\text{hydro}} + \FF_i^{\text{repul}},\quad
  T_i = T_i^{\text{hydro}} + T_i^{\text{repul}}, \qquad
  i=1,\ldots,N_b.
\end{align}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Time Marching}
By solving the mobility problem, we obtain translational and angular
velocities of the $N_b$-body system. 
A second-order Adams-Bashforth
scheme updates the particle positions and orientations. By including the
repulsion force~\eqref{eq:REPULforce}, particle collisions are avoided even
when using a relatively large time step.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{HAP Boundary Integral Equation}
Similar to our previous work (\cite{Fu20}), we represent the HAP as a
double-layer potential
\begin{align}
  \label{eq:HAP_DLP}
  u(\xx) = \frac{1}{2\pi} \int_{\bd\Omega} \pderiv{}{\nnu_\yy}
    K_0 \left(\frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) \, \dif s_\yy,
    \quad \xx \in \Omega,
\end{align}
where $K_0$ is the zeroth-order modified Bessel function of the first
kind and the integral is taken in the sense of principle value whenever $\xx \in \partial \Omega$. 
By requiring that the density function $\sigma$ satisfies the
second-kind integral equation
\begin{equation}
\label{eq:screenedSKIE}
  f(\xx) = \frac{1}{2}\sigma(\xx) + 
    \frac{1}{2\pi}\int_{\bd\Omega} \pderiv{}{\nnu_\yy}
    K_0 \left(\frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) \, \dif s_\yy,
    \quad \xx \in \bd\Omega,
\end{equation}
the HAP double-layer potential~\eqref{eq:HAP_DLP} satisfies the screened
Laplace equation~\eqref{eq:SL}--\eqref{eq:SLff}. After
discretizing~\eqref{eq:screenedSKIE}, the result is an $NN_b \times NN_b$
linear system that is solved with block-diagonal preconditioned GMRES.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Mobility Problem Boundary Integral Equation}
Following previous work of~\cite{Lukas19}, we use the velocity
representation of~\cite{pow-mir1987}. In particular, we write the
velocity as the sum of a double-layer potential and $N_b$-many Stokeslets and
rotlets
\begin{align}
  \label{eq:velocity}
  \uu(\xx) = \uu_\infty(\xx) + \DD[\eeta](\xx) + 
    \sum_{i=1}^{N_b} \left(\SS(\xx,\aa_i) \FF_i + 
    \RR(\xx,\aa_i) T_i\right), \quad \xx \in \Omega.
\end{align}
The double-layer potential is
\begin{align}
  \DD[\eeta](\xx) = \frac{1}{\pi} \int_{\bd\Omega} 
    \frac{\rr \cdot \nnu}{|\rr|^2} \frac{\rr \otimes \rr}{|\rr|^2}
    \eeta(\yy) \, \dif s_\yy,
\end{align}
where $\rr = \xx - \yy$ and $\rho = |\rr|$. The Stokeslet and rotlets
centered at $\aa_i$ are
\begin{align}
  \SS(\xx,\aa_i)\FF_i &= \frac{1}{4\pi} \left(-\log |\rr| + 
    \frac{\rr \otimes \rr}{|\rr|^2}\right) \FF_i, \\
  \RR(\xx,\aa_i)T_i &= \frac{1}{4\pi} \frac{\rr^\perp}{|\rr|^2} T_i,
\end{align}
respectively, where $\rr = \xx - \aa_i$. The
Stokeslet is torque-free and has force $\FF_i$ while the rotlet is
force-free and has torque $T_i$. Therefore, the
velocity~\eqref{eq:velocity} satisfies the total force~\eqref{eq:force}
and torque~\eqref{eq:torque} conditions if the double-layer potential
$\DD[\eeta]$ is force- and torque-free.  Matching the limit
of~\eqref{eq:velocity} with the rigid body motion, and imposing that
$\DD[\eeta]$ is force- and torque-free, the density function $\eeta$,
translational velocity $\vv_i$, and angular velocity $\omega_i$ satisfy
\begin{alignat}{3}
  \nonumber
  \vv_i + \omega_i (\xx - \aa_i)^\perp &= \uu_\infty(\xx)
    -\frac{1}{2} \eeta(\xx) + \DD[\eeta](\xx) \\
  \label{eq:SKIE}
    + \sum_{j=1}^{N_b} &
    \left(\SS(\xx,\aa_j) \FF_j + \RR(\xx,\aa_j) T_j\right),
    \quad &&\xx \in \Gamma_i,\: i=1,\ldots,N_b, \\
  \label{eq:mobility1}
  \int_{\bd\Gamma_i} \eeta \cdot \nnu_i \, \dif s &= {\bf 0}, 
  &&i = 1,\ldots,N_b, \\
  \label{eq:mobility2}
  \int_{\bd\Gamma_i} \eeta\times(\xx-\aa_i)^\perp \cdot \nnu_i \, \dif s &= 0,
  &&i = 1,\ldots,N_b.
\end{alignat}

After discretizing and applying appropriate quadrature rules, the result
is a $(2NN_b + 3N_b) \times (2NN_b + 3N_b)$ linear system that we solve
with block-diagonal preconditioned GMRES. Other BIE
formulations of the mobility problem have used single-layer potentials
(\cite{cor-gre-rac-vee2017, rac-gre2016}) or a combination of single-
and double-layer potentials (\cite{cor-vee2018}).

We validated our solver for \eqref{eq:SKIE}-\eqref{eq:mobility2} using a
single elliptical particle suspended in a background shear flow (see
\S~\ref{sec:ves_in_shear}). Hydrophobic attraction and repulsion are
zero for a single particle (see \cite{Fu20} equation 2.13). The angle of the ellipse's major axis coming
from the integral equation method was in complete agreement with the
theoretical, Jeffery orbit time-course (\cite{jef1922}).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Main Theoretical Result: Calculating the Hydrophobic Force}
\label{subsec:calculating_force}
Once \eqref{eq:screenedSKIE} has been solved for $\sigma$, we need to
evaluate the integrals~\eqref{eq:hydrophobicAttraction} which are the
HAP forces and torques. These integrals involve the
stress~\eqref{eq:stress} which contains a singular integral for the
gradient of the double-layer potential. To avoid singular integrals, we
first define
\begin{align}
  \label{eq:uidef}
  v_i(\xx) = u(\xx) - u_i(\xx),
\end{align}
where
\begin{align}
  u_i(\xx) &= \frac{1}{2\pi} \int_{\Gamma_i} \pderiv{}{\nnu_\yy}
    K_0 \left(\frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) \, \dif s_\yy,
    \quad \xx \in \mathbb{R}^2.
\end{align}
That is, $v_i(\xx)$ is the double-layer potential~\eqref{eq:HAP_DLP}
with $\Gamma_i$ excluded from $\bd\Omega$. Having defined $v_i$, we prove
\begin{theorem}
\begin{align}
  \label{eq:recipforcetorque}
  \FF_i^{\mathrm{hydro}} = \int_{\Gamma_i} \JJ_i \,\dif s,\quad
  T_i^{\mathrm{hydro}}    = \int_{\Gamma_i} 
    (\xx - \aa_i)^{\perp} \cdot \JJ_i  \,\dif s,
\end{align}
where
\begin{align}
  \label{eq:jumpstress1}
  \JJ_{i} = 2\gamma\rho^{-1} \sigma v_i \nnu + 
    2\gamma\rho \frac{d\sigma}{ds} \frac{dv_i}{ds} \nnu -
    2\gamma\rho \frac{d\sigma}{ds} \frac{dv_i}{d\nnu} \ttau.
\end{align}
\end{theorem}
The symbols $\ttau$ and $\frac{d}{ds}$ are the unit tangent and arc length
derivative for $\Gamma_i$, respectively (Figure \ref{fig:figure0}a.)  
The result 
is valid for any smooth particle shape or boundary condition. 
The advantage in using~\eqref{eq:recipforcetorque} over
using~\eqref{eq:hydrophobicAttraction} is that the components $\sigma$,
$v_i$, $\frac{d\sigma}{ds}$, and $\frac{dv_i}{ds}$ of $\JJ_i$ are smooth
functions, whereas the components of \eqref{eq:stress} are singular
integrals.

@@
